---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DRAGGER

<!-- badges: start -->
[![R-CMD-check](https://github.com/AEstebanMar/DRAGGER/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/AEstebanMar/DRAGGER/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

DRAGGER provides a toolkit for drug repositioning based on variant and gene-expression data. It includes a wrapper
for a basic workflow, but a custom run can be set up with ease.

## Installation

You can install the development version of DRAGGER from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AEstebanMar/DRAGGER")
```

## Example

DRAGGER includes a demo dataset to showcase its main use case.

```{r First few lines of demo datasets}
library(DRAGGER)
head(GWAS_demo)
head(GTEx)
head(DGIdb)
```

DRAGGER includes a wrapper function, aptly named DRAGGER, which executes the basic workflow.
Workflow is described in detail in vignettes, along with customisation options.

```{r DRAGGER_demonstration}
library(DRAGGER)
demo <- DRAGGER(GWAS_demo, GTEx, DGIdb)
head(demo)
```

Here is a preview of the type of plots included in DRAGGER, also heavily customisable.

```{r Basic_plot_demonstration}
library(DRAGGER)
demo <- suppressMessages(DRAGGER(GWAS_demo, GTEx, DGIdb))
plot_volcano(demo)
barplot_by_groups(demo, "rs_id", "candidate")
```
A small expasion of base-R chisq test is also included, and can provide insight
into DRAGGER results. The following example compares the number of RS with
a valid candidate by tissue, specifically brain vs stomach.

```{r test_chi2}
library(DRAGGER)
demo <- suppressMessages(DRAGGER(GWAS_demo, GTEx, DGIdb))
test_chi2(demo, "Tissue", "brain", "stomach",
      "candidate", TRUE, FALSE)
```